---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
body {
  font-size: 20px;
  background-color: #FFFFFF;
}
p {
  color: #333333;
}
h1, h2, h3 {
  font-weight: bold;
}
```

## My dynamic report is tracking regular transactions I observe, identifying the most frequent transaction methods, places, and times.

```{r}
# Reading data into R
URL <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vRZt32kU5Rgliiirpj4SxYxFhOmcQE1g1vJgZg8_deqjQLp1rDV0iheUa88-vODGOhoyToTxhGOtgqB/pub?gid=997753295&single=true&output=csv"
logged_data <- read_csv(URL)

# Renaming the variables
latest_data <- logged_data %>%
  rename(transaction_place = 2, transaction_amount = 3, transaction_method = 4, transaction_time = 5)
```

### Summary Values Output

```{r}
# Getting summary values
max_transaction_observed = max(latest_data$transaction_amount) # max amount observed
mean_transaction_amount = round(mean(latest_data$transaction_amount)) # mean of all transactions observed rounded to the nearest integer
```

The maximum amount of transaction that I have observed is `r max_transaction_observed` in NZ dollars.

The mean of all the transactions that I have observed, rounded to the nearest integer is `r mean_transaction_amount` in NZ dollars.

### Bar Charts

#### What is the most common place of transaction?

```{r}
# Most Common Place of Transaction Observed
place_common <- ggplot()+
  geom_bar(aes(x = latest_data$transaction_place), fill = "orange") +
  labs(title = "Most Common Places of Transaction", x = "Place", y = "Amount of Transactions Observed", caption = "Source: STATS 220 Project 2 Survey: Observing Transactions") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 7)) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(plot.caption = element_text(size = 7, hjust = 1)) +
  scale_y_continuous(limits=c(0,20))
place_common
```

Cafes and Restaurants tend to be the most common place of transactions as observed in my data.

#### What payment methods do people prefer the most?

```{r}
# Most Common Payment Method Observed
method_common <- ggplot()+
  geom_bar(aes(x = latest_data$transaction_method), fill = "blue") +
  labs(title = "Most Common Payment Methods", x = "Payment Method", y = "Amount of Transactions Observed", caption = "Source: STATS 220 Project 2 Survey: Observing Transactions") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 7)) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(plot.caption = element_text(size = 7, hjust = 1)) +
  scale_y_continuous(limits=c(0,30))
method_common
```

People generally prefer to use Card(Debit/Credit) for payments as observed in my data.

#### When do most transactions occur?

```{r}
# Most Common Time of the Day when Transactions Take Place
time_common <- ggplot()+
  geom_bar(aes(x = latest_data$transaction_time), fill = "green") +
  labs(title = "Most Common Time of The Day for Transactions", x = "Time of Day", y = "Amount of Transactions Observed", caption = "Source: STATS 220 Project 2 Survey: Observing Transactions") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 7)) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(plot.caption = element_text(size = 7, hjust = 1)) +
  scale_y_continuous(limits=c(0,20))
time_common
```

Most transactions happen during Afternoon as observed in my data.
